Using Traffic Analysis to Identify the Second Generation Onion Router

### 2011-06-26 thesis/results.tex
Add back in the fourth question from the proposal

>>>>

\subsection{How long does a user have to be connected to the network before a
confident match can be made?}

The basic algorithm designed using a simple heuristic approach matches on the
4th and 5th packets of an individual TCP session. Given that the first three
packets of any TCP session are the session negotiation packets, the
demonstrated algorithm only requires two packets before being confident of a
positive match. It is likely that this is far earlier than any user data has
had a chance to traverse the Tor network.
